\Title

### 2022-09-28 Grimaldi-etal-BiolCybernetics.tex
Introduction
Update on Overleaf.

Neuroscience could provide revolutionary answers to these two closely related problems. Indeed, the human brain has the remarkable property of being able to react at any time, while consuming a reasonable amount of energy, estimated at 5W at rest. This system is the result of millions of years of natural selection, and a striking difference between biological neural networks and artificial ones is the representation they use. CNNs, for example, represent information passing from one layer to another as tensors representing visual information densely over the visual topography, while representing different properties in different channels. On the other hand, information in a large majority of biological neural networks is represented as spikes, i.e. prototypical all-or-nothing events whose only parameters are their timing and the address of the neuron that emitted this spike. Why spikes? It is not yet known why most biological systems have evolved to use this representation, but one major advantage seems to be some form of efficiency. In the human brain, each of the approximately ten trillion nerve cells emits on average one spike per second, but each neuron fires with great variability, and up to 300 spikes per second. Many attempts have been made to build artificial spiking neural networks, and in particular to achieve the same performance as observed in classical CNNs, but with a lower energy budget. However, none of these networks has yet surpassed the state of the art performances. Here, we will try to focus on a property of spike neurons inspired by neurobiology to progress in this direction.
%
\subsection{What can neuroscience bring to computer vision?}% and the hetero-synaptic delays in spiking neurons}
%%%-----------------------------------------------------------------
Let us first focus on some existing spiking neural network models. A first motivation for these models was to understand biological observations at different scales. For example, the Hodgkin-Huxley model describes the dynamics of the membrane potential and the role of different voltage-dependent ion channels. It also explains how the model can produce a spike. Larger scale models introduce an explicit spiking mechanism, for example in the Integrate-and-Fire model. It predicts the emergent states of a recurrently connected neural network (Brunel). Several models have increased the scale of the system to include more neurons, such as the Virtual Brain (Sanz), which mixes spike neural networks with analog neural mass models. However, these methods are mainly descriptive with applications in neuroscience but few have had an application in computer vision. Another class of approaches have designed spiking neural networks that aim to have applications in machine learning. One of these is the SpikeNet algorithm which uses a radical approach by encoding information using one spike per neuron (Delorme). Another type of spiking neural network attempts to determine the structure of the network in order to minimize a cost function. This was implemented in the SpikeProp algorithm (Bohte) and is now widely used in methods that attempt to transfer performance from CNNs to SNNs, for example using a surrogate gradient approach. However, the performance of SNNs is still lower than that of analog networks and the question of the advantage of using spikes remains open.

@@

@@

\note{show the gap:}

>>>>

Neuroscience could provide revolutionary answers to these two closely related problems. Indeed, the human brain has the remarkable property of being able to react at any time, while consuming a reasonable amount of energy, estimated at 5W at rest. This system is the result of millions of years of natural selection, and a striking difference between biological neural networks and artificial ones is the representation they use. CNNs, for example, represent information passing from one layer to another as tensors representing visual information densely over the visual topography, while representing different properties in different channels. On the other hand, information in a large majority of biological neural networks is represented as spikes, i.e. prototypical all-or-nothing events whose only parameters are their timing and the address of the neuron that emitted this spike. Why spikes? It is not yet known why most biological systems have evolved to use this representation, but one major advantage seems to be some form of efficiency. In the human brain, each of the approximately 90 trillion nerve cells emits on average one spike per second to an average of 10000 synapses, but each neuron fires with great variability, and up to 300 spikes per second. Many attempts have been made to build artificial spiking neural networks, and in particular to achieve the same performance as observed in classical CNNs, but with a lower energy budget. However, none of these networks has yet surpassed the state of the art performances. Here, we will try to focus on a property of spike neurons inspired by neurobiology to progress in this direction.
%
\subsection{What can neuroscience bring to computer vision?}% and the hetero-synaptic delays in spiking neurons}
%%%-----------------------------------------------------------------
Let us first focus on some existing spiking neural network models. A first motivation for these models was to understand biological observations at different scales. For example, the Hodgkin-Huxley model describes the dynamics of the membrane potential and the role of different voltage-dependent ion channels. It also explains how the model can produce a spike. Larger scale models introduce an explicit spiking mechanism, for example in the Integrate-and-Fire model. It predicts the emergent states of a recurrently connected neural network (Brunel). Several models have increased the scale of the system to include more neurons, such as the Virtual Brain (Sanz), which mixes spike neural networks with analog neural mass models. However, these methods are mainly descriptive with applications in neuroscience but few have had an application in computer vision. Another class of approaches have designed spiking neural networks that aim to have applications in machine learning. One of these is the SpikeNet algorithm which uses a radical approach by encoding information using one spike per neuron (Delorme). Another type of spiking neural network attempts to determine the structure of the network in order to minimize a cost function. This was implemented in the SpikeProp algorithm (Bohte) and is now widely used in methods that attempt to transfer performance from CNNs to SNNs, for example using a surrogate gradient approach. However, the performance of SNNs is still lower than that of analog networks and the question of the advantage of using spikes remains open.

@@

normarive models

@@
